Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-06 paper.qmd
Initial work on the effect of density

## Compute error
error_df_two_curvy_abs <- augment(
  df_bin_centroids = df_bin_centroids2,
  df_bin = df_bin_two_curvy2,
  training_data = training_data_two_curvy,
  newdata = NULL,
  type_NLDR = "UMAP",
  col_start = "x")

@@

>>>>

## Compute error
error_df_two_curvy_abs <- augment(
  df_bin_centroids = df_bin_centroids2,
  df_bin = df_bin_two_curvy2,
  training_data = training_data_two_curvy,
  newdata = NULL,
  type_NLDR = "tSNE",
  col_start = "x")

@@

```{r}
source("scripts/one_c_shaped_dens_structure/04_gen_error_plots.R")
```

```{r}
#| fig-height: 5
#| fig-width: 15
#| fig-pos: H
generate_error_plots_one_c_shaped()
```
